Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
Changement d'indentation
Modification de partie 4

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps : establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.
\section{Related works}

@@

    The fields that are being used here are described in Table~\ref{table:data_columns}.

    This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}.

@@

    \begin{table}[!b]
        \centering
        \caption{Summary of technologies}
        \label{table:techno_numbers}
        \begin{tabular}{cccccc}
            \toprule
            \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
            \cmidrule(lr){1-6}
            \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
            \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
            \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
            \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
            \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
            \bottomrule
        \end{tabular}
    \end{table}

@@

    \begin{table}[!b]
        \centering
        \caption{Description of the dataset}
        \label{table:data_columns}
        \begin{tabular}{ll}
            \toprule
            \textbf{Column} & \textbf{Description} \\
            \cmidrule(lr){1-2}
            \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
            \textsl{nom\_op} & Name of the provider \\
            \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
            \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
            \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
            \bottomrule
        \end{tabular}
    \end{table}

@@

    Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, $4G$.

\section{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each \acrfull{bs}.
For that, we will construct a neigbouring graph $G = (P, U)$ (each base station that are considered neighbors are
connected by an edge) where $P$ is the set of all base stations. 
Here are the different methods we can build this graph with:

\subsection{$k$-NN graph}
\noindent The most intuitive method is to connect each \acrshort{bs} to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ 
is a parameter to be fixed.

However, this method can be criticized, because it always finds $k$ neighbor to each base stations, no matter the reality of the 
data.

\subsection{Delaunay triangulation}
\noindent The Delaunay triangulation is named after Boris DELAUNAY for his work on it from 1934 \cite{art_delaunay}.

A Delaunay triangulation of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points. You can find an illustration of this method in Figure~\ref{fig:del_tri}.

@@

The Delaunay triangulation is the pendant of the Voronoi diagram in the sense that two points are connected in the
Delaunay triangulation if their associated cells share an edge in the Voronoi diagram.

Therefore, another approach, consists in computing a Delaunay triangulation and build a neighouring graph $G = (P, U)$ where $U$ 
is composed of every edge of $D(P)$. Which is equivalent to consider two base station as potential neighbors if their associated
cells are touching each other in the Voronoi diagram.

This method has already been used in articles in the past \cite{delaunay_neighbor}.

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi tessellation (in red)}
    \label{fig:del_tri}
\end{figure}

\subsection{Gabriel graph}
\noindent The Gabriel graph is a subgraph of a Delaunay triangulation. Thus, if the Delaunay triangulation is given, it can be found in a linear time.

Gabriel graphs are named after K. Ruben Gabriel, who introduced them in a paper with Robert R. Sokal in 1969 \cite{10.2307/2412323}.

Formally, it is the graph $G = (P, U)$ in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.

@@

@@

Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories :
\begin{itemize}
    \item \emph{city center};
    \item \emph{urban area};
    \item \emph{extra-urban area};
    \item \emph{countryside}.
\end{itemize}

@@

It consists in detecting clusters based on the density, using two parameters :

\begin{itemize}
    \item \emph{$\varepsilon$} : A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$} : The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.

\end{itemize}

@@

Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
values could be modified.

@@

\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_qua}
\end{figure}

@@

@@

[Ouverture : prendre en compte les zazimuths]

>>>>

    For that, it is necessary to describe and analyse the databases that have been used during the research, then to present 
    the different approaches that always consist of these steps: establish a first neighbouring graph, compute the base station 
    densities and filter this graph with different criteria using this information. The final step is to present the results
    of the different approaches and conclude.
\section{Related works}

@@

The fields that are being used here are described in Table~\ref{table:data_columns}. [expliquer qu'il y x colonnes mais qu'on utilise que elles]

This database is updated every quarter. For instance, the own we used was published on 28\textsuperscript{th} March 2024 \cite{main_database_hist}. [dire depuis quand la base existe]

@@

[parler des technologies, rajouter des graphes]

\begin{table}[!b]
    \centering
    \caption{Number of \acrfull{bs} equipped, at least, with $x$G, by provider}
    \label{table:techno_numbers}
    \begin{tabular}{cccccc}
        \toprule
        \textbf{Technology} & \textbf{Bouygues} & \textbf{Free} & \textbf{Orange} & \textbf{SFR} & \textbf{Total} \\
        \cmidrule(lr){1-6}
        \textbf{2G} & 21710 & 0 & 18835 & 20093 & 60638 \\
        \textbf{3G} & 26294 & 25934 & 29748 & 25777 & 107753 \\
        \textbf{4G} & 26231 & 25847 & 30440 & 25881 & 108399 \\
        \textbf{5G} & 11271 & 18607 & 8794 & 10968 & 49640 \\
        \textbf{Total} & 26331 & 25949 & 30540 & 26018 & 108838 \\
        \bottomrule
    \end{tabular}
\end{table}

@@

\begin{table}[!b]
    \centering
    \caption{Description of the main database columns used in the experiments}
    \label{table:data_columns}
    \begin{tabular}{ll}
        \toprule
        \textbf{Column} & \textbf{Description} \\
        \cmidrule(lr){1-2}
        \textsl{id\_station\_anfr} & \acrshort{anfr} \acrshort{bs} ID \\ 
        \textsl{nom\_op} & Name of the provider \\
        \textsl{x, y, latitude, longitude} & Base station coordinates \\ 
        \textsl{nom\_reg, nom\_dep, nom\_com} & Additional location information \\  
        \textsl{site\_2g, 3g, 4g, 5g} & Technology used by the \acrshort{bs} \\ 
        \bottomrule
    \end{tabular}
\end{table}

@@

Secondly, for the same reasons as before, only one technology is kept. Thus, we kept all \acrshort{bs} using, at least, 4G.

Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
\section{Reminder on existing methods}
\subsection{Finding potential neighbours}
\noindent When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

\subsubsection{$k$-NN graph}
The most intuitive method is to connect each point to its $k$ nearest neighbours, where $k \in \mathbb{N}^*$ is a parameter to be fixed.

However, this method can be criticised, because it always finds $k$ neighbours for each point, no matter the reality of the 
data.

\subsubsection{Delaunay triangulation}
A Delaunay triangulation \cite{art_delaunay} of a set of points in the plane subdivides their \gls{convHull} into triangles whose circumcircles 
do not contain any of the points.

@@

It is a well-known method when trying to find neighbours \cite{delaunay_neighbor}
since a Delaunay triangulation is the pendant of a Voronoi diagram, cf. Figure~\ref{fig:del_tri}, i.e. two points are connected in the
Delaunay triangulation if their associated cells are touching each other in the Voronoi diagram.

\begin{figure}[!t]
    \centering
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_circumcircles_vectorial.png}}
    \boxed{\includegraphics[width=1.25in]{images/illus_graphs/Delaunay_Voronoi.png}}
    \caption{Example of a Delaunay triangulation (in black) and Voronoi diagram (in red)}
    \label{fig:del_tri}
\end{figure}

\subsubsection{Gabriel graph}
A Gabriel graph \cite{10.2307/2412323} is a subgraph of a Delaunay triangulation. Thus, if the Delaunay triangulation is given, it can be found in a linear time.

Formally, it is the graph in which any two distinct points $p, q \in P$ are adjacent precisely when the closed disc having $pq$ as a diameter contains no other points.

@@

\subsection{Finding real neighbours}
\noindent For the purpose of our experiments, i.e. finding \acrshort{bs} neighbours, the previously presented methods are not sufficient to find real neighbours.
As a consequence, some neighbouring connexions needs to be suppressed \cite{patent_neighs}.
\subsubsection{Distance criterion\cite{patent_neighs}}
A \acrshort{bs} does not have an infinite coverage area.
As a consequence, each edge in $U$ that is longer than a certain value, called \emph{max\_distance}, is suppressed.

Therefore, the connexion between $p$ and $r$ needs to be suppressed. How? The angle $\widehat{qrp}$ is calculated and if it is narrower than a certain value, called \emph{min\_angle}, the longest edge is suppressed.

\subsubsection{Quadrant criterion}
\begin{figure}[!b]
    \centering
    \boxed{\includegraphics[width=2.5in]{images/illus_crit/quadrant_elim.png}}
    \caption{Example of a Delaunay triangulation}
    \label{fig:crit_qua}
\end{figure}

As introduced in a previous article \cite{10201211} its goal is to prevent all potential neighbours to be in the same angle range. Therefore, it was mainly thought to be used with the 
$k$-NN potential neigbours method.

It consists in dividing the space around each base station into quadrants and keeping only a certain number of potential neighbours
in each of the quadrants, cf. Figure~\ref{fig:crit_qua}.
The number of quadrants has been fixed to six \cite{art_del_paq}.

\subsection{Density-based clustering methods}
\noindent Although the filtering methods are providing good results, it is still not enough.
Therefore, we will modify those criteria to take in account the variations of \acrshort{bs} density. Thus, we need some measurement of this density.

As those problems are equivalent and because this is simpler to visualise, we will say that we are looking for detecting the cities.
\subsubsection{\acrshort{dbscan}}
\acrshort{dbscan} consists in detecting clusters based on the density of points, using two parameters:
\begin{itemize}
    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
\end{itemize}

\subsubsection{\acrshort{hdbscan}}
\acrshort{hdbscan} \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
is that it allows to detect clusters of different densities.

To each point who belongs to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
to the said cluster.

@@

Moreover, to simplify the problem, each \acrshort{bs} will be classified in one of this four categories:
\begin{itemize}
    \item \emph{city center};
    \item \emph{urban area};
    \item \emph{extra-urban area};
    \item \emph{countryside}.
\end{itemize}

@@

It consists in detecting clusters based on the density, using two parameters:

\begin{itemize}
    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
\end{itemize}

@@

Moreover, this values are working well on France but it is not proven that it can work in another country. If someone uses this methods, 
values could be modified [dire que c'est plutot qqch à faire dans le futur et pas que c'est pas vérifié].

[Rajouter les catégories]

@@

@@

[Dire que c'est des angles adjacents]

@@

[Ouverture: prendre en compte les zazimuths]
